What about children's wellbeing? Framing active school travel in Ontario, Canada

### 2021-04-12 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Create markdown for Elsevier article

---
title: What about children's wellbeing? Framing active school travel in Ontario, Canada
author:
  # see ?rjournal_article for more information
  - name: Elise Desjardins
    affiliation: School of Earth, Environment & Society, McMaster University
    address:
    - 1280 Main Street West, Hamilton, ON L8S 4L8
    email: desjae@mcmaster.ca
  - name: Jason Lam
    email: lamj54@mcmaster.ca
    affiliation: Affiliation 1
    address:
    - line 1 affiliation 1
  - name: Owen Waygood
    affiliation: University Polytechnique de Montreal
    email: owen.waygood@polymtl.ca
    address:
    - Montreal, QC
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: Affiliation 1
    address:
    - line 1 affiliation
abstract: >
  An abstract of less than 200 words.
preamble: |
  % Any extra LaTeX you need in the preamble

journal: "Journal of School Health"
date: "`r Sys.Date()`"
bibliography: References.bib
#linenumbers: true
#numbersections: true
output: rticles::rjournal_article
---

# Background

Walking and cycling to school, commonly known as active school travel or active school transportation (AST) has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020]. This trend has prompted an abundance of worlwide research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health. Many studies have been specific to Canada [*inter alia*, see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in increasing active school travel levels. Indeed, a diversity of stakeholders responsible for transportation, public health, and education are collaborating and spearheading efforts to get more children walking and cycling. Promoting AST is seen as an affordable, convenient, and environmentally friendly way to enhance the mental, physical, and psychological health of children [@mammenSchoolTravelPlanning2014]. These goals should be clearly articulated and reflected in transportation plans and policies to guide initiatives, but there is research lacking that specifically explores how Canadian municipalities and schools frame and discuss AST with the public.

## Literature Review

@@

## Case Study: Ontario, Canada

@@

# Methods

## Procedure

### Approach to collecting data

There are three folders containing pdf documents from corresponding sources, consortiums, municipalities/regions, and school boards. Docurments are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible. Unique criteria was used for each source type to determine eligibility of documents. For all sources, however, it was important that webpages were fairly easy to find as the analysis pretains to how such issues are framed to the public.'Fairly easy' means webpages that are required several steps of search or navigation to find.

To start a list of all school boards in Ontario and their associated consortium and municipalitiy/region is created. This list is used as a guide and dictate the the search.

School boards generally will have a single page for transportation so documents were sourced from those pages regardless in mentioned STP or AST. In cases were both AST and STP are mentioned both those pages are included. 
Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevent to our analysis. Only pages specifically dicussing active travel, AST, or STP are included. Page were also sourced from associated local health units which were considered part of municpalities/regions

Consortiums are deicated transportation pages that primarly focus of providing the school bussing service to families. For this group it was determined that only relevent pages specifically relating to AST or STP would be included.

@@

### Import packages

```{r}
library(tm)
library(readr)
library(tools)
```

@@

## Data Analysis

# Results

# Discussion

## Limitations

## Conclusion

# Implications for School Health

Schools are an influential contributor to AST and STP efforts in Canada.

>>>>

---
title: What about children's wellbeing? Framing active school travel in Ontario, Canada
author:
  - name: Author 1
    email: author1@example.com
    affiliation: Some Department
    footnote: 1
  - name: Author 2
    email: author2@example.com
    affiliation: Some Department
  - name: Author 3
    email: author3@example.com
    affiliation: Another University
    footnote: 2
  - name: Author 4
    email: author4@example.com
    affiliation: Some Institute
    footnote: 2
  - name: Author 5
    email: author5@example.com
    affiliation: Some University
  - name: Author 6
    email: author6@example.com
    affiliation: Some Department
address:
  - code: Some Department
    address: Department, Street, City, Province, Postal Code
  - code: Another University
    address: Department, Street, City, Province, Postal Code
  - code: Some Institute
    address: Street, City, Province, Postal Code
  - code: Some University
    address: Department, Street, City, Province, Postal Code
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  This is the abstract.

  It consists of two paragraphs.

journal: "Journal of Transport & Health"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

```{r, include=FALSE}
library(tm)
library(readr)
library(tools)
```

1. Background
===============

Walking and cycling to school, commonly known as active school travel or active school transportation (AST) has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020]. This trend has prompted an abundance of worlwide research over the past two decades to examine why fewer children are walking and cycling to school, what influences AST, and the associated implications for children's health. Many studies have been specific to Canada [e.g., see: @buliungActiveSchoolTransportation2009; @faulknerSchoolTravelChildren2013; @mammenUnderstandingDriveEscort2012; @mammenSchoolTravelPlanning2014; @rothmanActiveSchoolTransportation2021; @wilsonUnderstandingChildParent2018] which aligns with and informs a growing interest in increasing active school travel levels. Indeed, a diversity of stakeholders responsible for transportation, public health, and education are collaborating and spearheading efforts to get more children walking and cycling. Promoting AST is seen as an affordable, convenient, and environmentally friendly way to enhance the mental, physical, and psychological health of children [@mammenSchoolTravelPlanning2014]. These goals should be clearly articulated and reflected in transportation plans and policies to guide initiatives, but there is research lacking that specifically explores how Canadian municipalities and schools frame and discuss AST with the public.

## 1.1. Literature Review

@@

## 1.2. Case Study: Ontario, Canada

@@

2. Methods
===============

## 2.1. Procedure

There are three folders containing pdf documents from corresponding sources, consortiums, municipalities/regions, and school boards. Documents are sourced from direct affiliate websites from those three groups and are printed to pdf via the web browser if deemed eligible. Unique criteria was used for each source type to determine eligibility of documents. For all sources, however, it was important that web pages were fairly easy to find as the analysis pertains to how such issues are framed to the public.'Fairly easy' means web pages that are required several steps of search or navigation to find.

To start a list of all school boards in Ontario and their associated consortium and municipality/region is created. This list is used as a guide and dictate the the search.

School boards generally will have a single page for transportation so documents were sourced from those pages regardless in mentioned STP or AST. In cases were both AST and STP are mentioned both those pages are included. 
Municipalities/regions would have often time pages about transportation that involved the service it provided which is not relevant to our analysis. Only pages specifically dicussing active travel, AST, or STP are included. Page were also sourced from associated local health units which were considered part of municipalities/regions

Consortiums are dedicated transportation pages that primarily focus of providing the school busing service to families. For this group it was determined that only relevant pages specifically relating to AST or STP would be included.

@@

@@

## 2.2. Data Analysis

3. Results
===============

4. Discussion
===============

# 4.1. Implications for School Travel Planning

School boards and educators are an influential contributor to AST and STP efforts in Canada.

## 4.2. Limitations

5. Conclusion
===============

References
===============
